\documentclass{amsart}
\usepackage{amsthm}
\usepackage{enumerate}




\newtheorem{theorem}{Theorem}
\newtheorem{problem}{Problem}
\newtheorem{remarks}{Remarks}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{step}{Step}
\newtheorem{case}{Case}
\newtheorem{definition}{Definition}
\newcommand{\ncc}{c}

\begin{document}
\author{Gao Mou}
\address{School of Physical and Mathematical Sciences, Nanyang Technological University, Singapore} 
\email{gaom0002@e.ntu.edu.sg} 
\author{Dmitrii V. Pasechnik}
\address{Department of Computer Science, The University of Oxford, UK}
\email{dimpase@cs.ox.ac.uk}

\title{On $k$-walks in $2K_2$-free graphs}
\begin{abstract}
We show that for any $\epsilon>0$ every $(\frac{1}{k-1}+\epsilon)$-tough
$2K_2$-free graph admits a $k$-walk, making a step towards proving a
long-standing conjecture from \cite{jackson1990k}. The proof uses a
decomposition of $2K_2$-free graphs which might be of independent interest.
\end{abstract}

\maketitle

\section{Introduction}

Let  $\ncc(G)$ denote the number of connected components of a graph $G$ with vertex set $V:=V(G)$ and edge set $E:=E(G)$. For $S\subset V$, let $G-S$ denote the subgraph of $G$ indiced on $V-S$.
\begin{definition}
$G$ is called $\beta$-{\em tough},
for a real $\beta>0$, if $\ncc(G-S)>1$ implies $|S|\ge \beta\cdot \ncc(G-S)$ 
for each $S\subset V$.
\end{definition}
That is, a $\beta$-tough 
$G$ cannot be split into $p$ (with $p>1$) components by removing less than
$p\beta$ vertices.  
This concept, a measure of graph connectivity and ``resilience'' under vertex subsets removal,
was introduced in 1973 by V. Chv\'{a}tal 
while studying   Hamiltonicity of graphs. For a survey of results on graph toughness till 2006
cf. \cite{MR2221006}. Our graph-theoretic notation is mostly from \cite{bomu08}.

In 1990 B.~Jackson and N.~Wormald conjectured \cite{jackson1990k} that every
$\frac{1}{k-1}$-tough graph $G$ admits a $k$-walk, i.e. a sequence of edges
visiting each vertex at least once and at most $k$-times, for any integer $k\ge2$. 

In this paper, we prove this conjecture is ``almost'' true, under the assumption that $G$ is  
$2K_2$-free, 
that is $G$ does not contain an induced copy of $2K_2$, i.e. the disjoint union of two edges.
Here by ``almost'' we mean that we need to replace
$\frac{1}{k-1}$-tough by $(\frac{1}{k-1}+\epsilon)$-tough, with $\epsilon>0$
arbitrarily small.
In fact $\epsilon$ can be set to 0 for most $2K_2$-free graphs, and the outcome of Theorem~\ref{thm2}
will remain true, cf. Theorem~\ref{opt} below for details.
\begin{theorem}\label{thm2}
For any $\epsilon>0$, and integer $k\ge2$,
every $(\frac{1}{k-1}+\epsilon)$-tough $2K_2$-free graph admits a $k$-walk. 
\end{theorem}

If we let the toughness value $\frac{1}{k-1}+\epsilon$ to increase to $\frac{1}{k-2}$ then
one does not need $2K_2$-freeness. Indeed, the following holds.
\begin{theorem}\cite{jackson1990k}\label{cthm1}
Every $\frac{1}{k-2}$-tough graph has a $k$-walk. 
In particular every 1-tough graph has a 3-walk. \qed
\end{theorem}
Clearly, if $G$ is
Hamiltonian, then $G$ is 1-tough, however, the converse is not true.  
More generally, note 
\begin{theorem}\cite{jackson1990k}\label{add}
If $G$ has a $k$-walk, then $G$ is $\frac{1}{k}$-tough. \qed
\end{theorem}

This more or less summarises the situation with $t$-tough graphs, $t\leq 1$.
On the $t>1$ side 
a famous conjecture of V.~Chv\'{a}tal \cite{chvatal1973tough} claims
that there exists a constant $\beta$ such that every
$\beta$-tough graph is Hamiltonian.  

The concept of a $k$-walk is a generalization of the concept of a Hamiltonian cycle.
Ellingham and Zha \cite{ellingham2000toughness} proved that
every 4-tough graph has a 2-walk.

Recently, in \cite{broersma2014toughness}, H.~Broersma, V.~Patel and A.~Pyatkin proved that 
every 25-tough 2$K_2$-free graph on at least three vertices is Hamiltonian.
Our Theorem~\ref{thm2} was inspired by this result.  
However, our
approach is technically quite different, and, unlike \cite{broersma2014toughness}, we do not seem to be
able to make any algorithmic conclusions about the problem at hand.
To prove Theorem~\ref{thm2}, we first prove the following.
\begin{theorem}\label{thm1}
For any $2K_2$-free graph $G$ the set $V(G)$ 
can be partitioned into three disjoint parts $V(Q_0)$, $V(Q_{\infty})$ and $V(D)$ (some of these parts possibly empty), so that for the corresponding induced subgraphs
$Q_0$, $Q_\infty$, and $D$ the following holds: $Q_0$ is dominating in $G$ and Hamiltonian, 
$Q_{\infty}$ admits a spanning path (also called Hamiltonian path), 
and $D$ is a coclique.
\end{theorem}
The terminology just used is standard; we include the following for the sake of clarity.
Here, a {\em clique} means a complete subgraph, a {\em coclique} means a
induced subgraph containing no edge. Let 
$A=\{v_1,\ldots,v_m\}\subseteq V$. A subgraph $P$ in $G$ with $V(P)=A$
and $E(P)=\{v_1v_2,v_2v_3,\ldots,v_{m-1}v_m\}$
is called a {\em path}.
For any $v\in V$, let 
$v^\perp:=v^{\perp_G}$ denote the union of $\{v\}$ and the set of neighbors of $v$ in $G$. 
More generally, 
for $A\subset V$, let $A^\perp:=A^{\perp_G}$ denote the set of vertices {\em dominated}
by $A$, i.e. $A^\perp=\bigcup\limits_{y\in A}v^\perp$, and
$A$ is said to be {\em dominating} if $A^\perp=V$. 
It should also lead to no confusion when we talk about  
dominating induced subgraphs $H$ of $G$, in the sense of $V(H)$ being
dominating, respectively
a subset of vertices (e.g. set of vertices of a subgraph) being dominated by $H$, etc.

\section{Properties of $2K_2$-free Graphs and Proof of Theorem \ref{thm1}}
An induced subgraph $H$ of $G$ with $B=V(H)$ (resp. $B\subset V$) is said to be {\em weakly-dominating}
an induced subgraph $F$ (we allow $F=G$ here) 
if for any $v_1v_2\in E(F)$, we have $v_1\in B^\perp$ or $v_2\in B^\perp$.
Further, let $\omega(G)$ denote the maximum size of cliques in $G$. 

\subsection{Properties of $2K_2$-free Graphs}
The following properties of $2K_2$-free graphs are very useful in the proof of Theorem \ref{thm1} and Theorem \ref{thm2}.

\begin{theorem}\label{trivial}
A graph $G$ is $2K_2$-free if and only if each edge in $G$ is weakly-dominating. \qed
\end{theorem}
The proof of this statement is trivial.

\begin{lemma}\label{lm1}{\cite[Theorem 2.]{chung1990maximum}\cite[Lemma 2.]{broersma2014toughness}}
Assume that $G$ is $2K_2$-free, $\omega(G)=2$, then $G$ is in one of the following cases.
\begin{enumerate}
\item $G$ is a bipartite.
\item $G$ can be obtained from a five-circle by vertex multiplication. \qed
\end{enumerate}
\end{lemma}



\begin{lemma}\label{lm2}{\cite[Theorem 3.]{chung1990maximum}}
If $G$ is $2K_2$-free and the maximum size of cliques $\omega(G)\ge3$, then $G$ has a dominating clique of size $\omega(G)$. \qed
\end{lemma}

\begin{lemma}\label{lm3}{\cite[Observation 1.]{broersma2014toughness}}
A graph $G=(V,E)$ is $2K_2$-free if and only if for every $A\subset V$, at most one component of the graph $G-A$ contains edges. \qed
\end{lemma}






Given a $2K_2$-free graph, assuming $\omega(G)\ge3$, by Lemma \ref{lm2}, we can find one of its maximum dominating clique, namely $Q_1$. Obviously, any induced subgraph of a $2K_2$-free graph is also $2K_2$-free. Then $G-Q_1$ is also a $2K_2$-free graph. By Lemma \ref{lm3}, $G-Q_1$ is made up by two parts, one is an independent subset (possibly empty) of $G-Q_1$, denoted by $D_1$, another part is a non-trivial component (possibly does not exist), denoted by $G_1$, which is also $2K_2$-free. For the same reason, we can find a maximum dominating clique in $G_1$ namely $Q_2$, and a non-trivial component in $G_1-Q_2$, namely $G_2$ and an independent subset in $G_1-Q_2$ namely $D_2$. During such process, possibly, there is a subscript $m$ such that $\omega(G_m)=2$ (such a $m$ may not exist). Then, we find a weakly-dominating clique $Q_{m+1}$ in $G_m$. Also, we get a non-trivial component in $G_m-Q_{m+1}$, namely $G_{m+2}$ and an independent subset in $G_m-Q_{m+1}$, namely $D_{m+1}$, and so on.

Then we have proved:
\begin{lemma}\label{lm5}
For a $2K_2$-free graph $G=G_0$, we can find a sequence of cliques $\{Q_i;i=1,\ldots,m+s\}$, where $|Q_i|\ge3$ when $1\le i\le m$ and $|Q_i|=2$ when $i=m+1,\ldots,m+s$. Additionally, $|Q_i|\ge|Q_{i+1}|$ for any $i$. $Q_i$ is a maximum dominating clique in $G_{i-1}$ when $i\le m$, and $Q_i$ is weakly-dominating clique (edge) in $G_{i-1}$ when $i>m$.
\end{lemma}


In addition, we get:

\begin{lemma}\label{lm6}
The vertex set of a $2K_2$-free graph $G$ can be divided into three disjoint parts:
\begin{enumerate}
\item $V(Q_0)=\cup_{i=1,\ldots,m}V(Q_i).$
\item $V(Q_{\infty})=\cup_{i=m+1,\ldots,m+s}V(Q_i).$
\item $V(D)=\cup_{i=1,\ldots,m+s}V(D_i)$
\end{enumerate}
Here, $Q_0$ is the induced subgraph of $G$ on the vertex set $V(Q_0)$, $Q_{\infty}$ is the induced subgraph of $G$ on the vertex set $V(Q_{\infty})$ and $D$ is the induced subgraph of $G$ on the vertex set $V(D)$. And we denote $V(Q)=V(Q_0)\cup V(Q_{\infty})$, where $Q$ is the induced subgraph of $G$ on the vertex set $V(Q)$. Obviously, $V(G)=V(Q)\cup V(D)$. Note that we allow any of these sets talked above to be empty.
\end{lemma}








\subsection{Spanning Path in The Induced Subgraph $Q_{\infty}$ Made up by All Cliques of Size 2}
Now, let us look at the behavior of all the cliques of size 2.
\begin{theorem}\label{thm4}
For a $2K_2$-free graph $G$, $Q_{\infty}$, as defined in Lemma \ref{lm6}, is the induced subgraph on all the vertices of all the 2-cliques in a maximum (weakly) dominating sequence. 
Then $Q_{\infty}$ admits a spanning path, i.e. a path visiting each vertex in $Q_{\infty}$ exactly once.
\end{theorem}


\begin{proof}
Denote $Q_{m+i}=v_{i,1}v_{i,2}$ for $i=1,\ldots,s$. By definition, $\omega(Q_{\infty})=2$.
\begin{enumerate}

\item If $Q_{\infty}$ is a bipartite, denote the two independent part as $B_1=\{v_{i,1};i=1,\ldots,s\}$ and $B_2=\{v_{i,2};i=1,\ldots,s\}$. 


Denote $Q^t_{\infty}$ as an induced subgraph of $Q_{\infty}$ containing $t$ of the edges $\{Q_{m+i}:i=1,\ldots,s\}$, i.e. let $V(Q^t_{\infty})=\{v_{i,j}:i=1,\ldots,t;~j=1,2\}$
Now let us make an induction on the size $t$. We shall prove in each of the $Q^t_{\infty}$, $(t=1,\ldots,s)$, there is a spanning path $v'_{1,1}v'_{1,2}v'_{2,1}\cdots v'_{t,1}v'_{t,2}$ and each edge $v'_{p,1}v'_{p,2}$ is some edge $Q_{m+q}=v_{q,1}v_{q,2}$.


If $t=1$, then $v_{1,1}v_{1,2}$ is the path we want. Now, we assume that $Q^t_{\infty}$, whose vertex set $V(Q^t_{\infty})=\cup_{i=1,\ldots,t}V(Q_{m+i})$, admits a spanning path, namely $v'_{1,1}v'_{1,2}\cdots v'_{t,1}v'_{t,2}$, with each $v'_{p,1}v'_{p,2}=v_{q,1}v_{q,2}$ for some $q$. Then let us look at a larger induced subgraph $Q^{t+1}_{\infty}$, with $V(Q^{t+1}_{\infty})=V(Q^t_{\infty})\cup\{v_{t+1,1},v_{t+1,2}\}$.

If $v'_{t,2}v_{t+1,1}\in E(G)$, we get the spanning path in $Q^{t+1}_{\infty}$, 
namely\\ $v'_{1,1} v'_{1,2}\cdots v'_{t,2} v_{t+1,1} v_{t+1,2}$.

If $v'_{1,1}v_{t+1,2}\in E(G)$, we get the spanning path in $Q^{t+1}_{\infty}$, 
namely\\ $v_{t+1,1} v_{t+2,2} v'_{1,1} v'_{1,2} v'_{2,1}\cdots v'_{t,2}$.

If $v'_{t,2}v_{t+1,1},v'_{1,1}v_{t+1,2}\not\in E(G)$, from the weakly-dominating property we get $v'_{t,1}v_{t+1,2}\in E(G)$ and $v'_{1,2}v_{t+1,1}\in E(G)$. Now, we denote $q$ as the smallest subscript for $v'_{q,1}v_{t+1,2}\in E(G)$. That means $v'_{q-1,1}v_{t+1,2}\not\in E(G)$. Again, by the weakly-dominating property, we get $v'_{q-1,2}v_{t+1,1}\in E(G)$. Then, we get a spanning path in $Q^{t+1}_{\infty}$, namely $$v'_{1,1}\cdots v'_{q-1,2}v_{t+1,1}v_{t+1,2}v'_{q,1}\cdots v'_{t,2}.$$

Thus, by mathematical induction, we know that $Q_{\infty}$ has a spanning path, with all the edges $Q_{m+i},i=1,\ldots,s$ are in the path.

\item If $Q_{\infty}$ is not a bipartite, by Lemma \ref{lm1}, $Q_{\infty}$ can be obtained from a five-circle by vertex multiplication. We denote $V(Q_{\infty})=V_1\cup V_2\cup V_3\cup V_4\cup V_5$, and $E(Q_{\infty})=E_1\cup E_2\cup E_3\cup E_4\cup E_5$, where each $V_i$ is an independent set, and  for any two vertices $v_1\in V_i$ and $v_2\in V_{i+1}$ (we consider $V_6=V_1$), we have an edge $e\in E_i$, such that $e=v_1v_2$. We denote $E'=\{v_{i,1}v_{i,2};i=1,\ldots,s\}$, and $E'_i=E_i\cap E'$. Obviously, $|V_i|=|E'_{i-1}|+|E'_i|$. Please note $|V_i|>0$ for $i=1,2,3,4,5$, otherwise, $Q_{\infty}$ is a bipartite. Thus for any $i$, $|E'_i|$ and $|E'_{i+1}|$ cannot be both 0. Without loss of generality, we can assume $|E'_1|,|E'_3|,|E'_5|>0$ and $|E'_2|,|E'_4|\ge0$.

 So, the vertices in the five subset $V_i$ can be denoted as following:

$$V_1=\{v_{1,j};j=1,\ldots,|E'_1|+|E'_5|\},$$
$$V_2=\{v_{2,j};j=1,\ldots,|E'_1|+|E'_2|\},$$
$$V_3=\{v_{3,j};j=1,\ldots,|E'_2|+|E'_3|\},$$
$$V_4=\{v_{4,j};j=1,\ldots,|E'_3|+|E'_4|\},$$
$$V_5=\{v_{5,j};j=1,\ldots,|E'_4|+|E'_5|\},$$
note that $|E'_2|$ and $|E'_4|$ are possibly 0.

Now, we get the spanning path:

$$v_{1,1}v_{2,1}v_{1,2}v_{2,2}\cdots v_{1,|E'_1|}v_{2,|E'_1|}v_{3,1}$$
$$v_{2,|E'_1|+1}v_{3,2}\cdots v_{2,|E'_1|+|E'_2|}v_{3,|E'_2|+1}v_{4,1}v_{3,|E'_2|+2}v_{4,2}\cdots v_{3,|E'_3|+|E'_2|}$$
$$v_{4,|E'_3|}v_{5,1}v_{4,|E'_3|+1}v_{5,2}v_{4,|E'_3|+2}\cdots v_{4,|E'_3|+|E'_4|}$$
$$v_{5,|E'_4|+1}v_{1,|E'_1|+1}v_{5,|E'_4|+2}v_{1,|E'_1|+2}\cdots v_{5,|E'_4|+|E'_5|}v_{1,|E'_1|+|E'_5|}.$$

Please note that if $|E'_2|=0$, the section $$v_{3,1}v_{2,|E_1'|+1}v_{3,2}\cdots v_{2,|E'_1|+|E'_2|}v_{3,|E'_2|+1}v_{4,1}$$ in the path is shortened to $v_{3,1}v_{4,1}$. And if $|E'_4|=0$ then the section $$v_{5,1}v_{4,|E'_3|+1}v_{5,2}v_{4,|E'_3|+2}\cdots v_{4,|E'_3|+|E'_4|}v_{5,|E'_4|+1}v_{1,|E'_1|+1}$$ in the path is shortened to $v_{5,1}v_{1,|E'_1|+1}$.
\end{enumerate}\end{proof}

\subsection{The proof of Theorem \ref{thm1}}
By Lemma \ref{lm6} and Theorem \ref{thm4}, we only need to prove that $Q_0$ is Hamiltonian.
The proof is divided into two parts. In the first part, we construct an auxiliary graph, a cycle, namely $\Gamma$. In the second part, with the help of $\Gamma$, we find a subgraph $H$ of $Q_0$,  which is the Hamiltonian cycle we want.
\subsubsection{Three trivial cases}
\begin{enumerate}
\item If $G$ is triangle-free, then $Q_0$ does not exist at all, then there is nothing to prove.
\item If there is only one clique, as defined in Lemma \ref{lm5}, with size at least 3, i.e. $Q_0=Q_1$, then obviously $Q_0$ is Hamiltonian, since it is just a clique.
\item If there are only two cliques, as defined in Lemma \ref{lm5}, with size at least 3, i.e. $V(Q_0)=V(Q_1)\cup V(Q_2)$, then choose an edge $v_1v_2$ from $Q_2$. We claim that $v_1$ and $v_2$ are adjacent to at least $|Q_1|-1$ vertices in $Q_1$. Otherwise, if there are two vertices $v_3$ and $v_4$ in $Q_1$ are adjacent neither $v_1$ nor $v_2$, then $v_1v_2$ and $v_3v_4$ form a $2K_2$.

Since $|Q_1|-1\ge2$, then we can choose two distinct vertices in $Q_1$, namely $v_5$ and $v_6$ such that $v_1v_5,~v_2v_6\in E(G)$. And we have a path in  $Q_1$, with $v_5$ and $v_6$ as endpoints and visiting each vertex in $Q_1$ exactly once, and also a path in $Q_2$, with $v_1$ and $v_2$ as endpoints and visiting each vertex in $Q_2$ exactly once.

Then these two paths and $v_1v_5$ and $v_2v_6$ form the Hamiltonian cycle we want.
\end{enumerate}

\subsubsection{The construction of $\Gamma$}

Now, we assume there are at least three cliques, as defined in Lemma \ref{lm5}, of size at least 3, i.e. $m\ge3$.

First, the vertex set of $\Gamma$, $V(\Gamma)=\{u_1,\ldots,u_m\}$, each $u_i$ corresponds to $Q_i$. 
Then we connect all these $u_i$ (i=1,\ldots,m) with a cycle, and we call this cycle $\Gamma$.




\subsubsection{The construction of $H$}
Now, with the help of $\Gamma$, we are going to find a Hamiltonian cycle in $Q_0$. 
The construction of $H$ is divided into two steps. In the first step, we find some {\bf green edges} in $Q_0$ corresponding to the edges in $\Gamma$. In the second step, we draw a path with {\bf yellow edges} in each $Q_i$, $i=1,\ldots,m$. Then the green edges and the yellow paths will make the Hamiltonian cycle in $Q_0$.

For the first step:

For any edge $u_iu_j$ $(1\le i<j\le m)$, we want to realize it into $H$ as a {\bf green edge}. Let us look at $Q_j$ first. We know that $u_j$ is incident to two edges in $\Gamma$, so there is only one vertex in $Q_j$, say $v_{j,1}$, is incident to another green edge. And $|Q_j|\ge3$, so there are at least two vertices $v_{j,2}$ and $v_{j,3}$ other than $v_{j,1}$ in $Q_j$. Both of $v_{j,2}$ and $v_{j,3}$ are dominated by $Q_i$. Then we claim that $v_{j,2}$ and $v_{j,3}$ have at least two neighbors in $Q_i$. Otherwise, if $v_{j,2}$ and $v_{j,3}$ have only one neighbor in $Q_i$, by $|Q_i|\ge3$, we know there are at least two vertices, say $v_{i,1}$ and $v_{i,2}$, who are adjacent to neither $v_{j,2}$ nor $v_{j,3}$. Then $v_{j,2}v_{j,3}$ and $v_{i,1}v_{i,2}$ form a $2K_2$.

Now we can assume $v_{j,2}v_1,~v_{j,3}v_2\in E(G)$, where $v_1,~v_2\in Q_i$. What is more, in $v_1$ and $v_2$, there is at most one of them, say $v_1$, is incident to another green edge, since there are only two edges incident to $u_i$ in $\Gamma$. Then we select $v_{j,3}v_2$ into $H$ as a {\bf green edge}.

From this process, we garantee that each vertex in $Q_0$ is incident to at most one green edge in $H$.

For the second step:

Here we want to find a path, in each $Q_i$, $i=1,\dots,m$, of {\bf yellow edges}, after adding all the green edges.

For any $Q_i$, there are two distinct vertices incident to green edges, denoted as $v_{i,a}$ and $v_{i,b}$. Because $Q_i$ is a clique, so we can find a path in $Q_i$ with endpoints $v_{i,a}$ and $v_{i,b}$ and visiting each vertex in $Q_i$ exactly once. All the edges in this path are called {\bf yellow edges}.

Obviously, all the green edges and yellow edges together here make a Hamiltonian cycle in $Q_0$.  \qed

\section{The Proof of Theorem \ref{thm2}}

For an integer $p$, let $p*G$ denote the multigraph obtained from $G$ by taking each edge $p$ times. 
Thus a $k$-walk is a subgraph of $(2k)*G$. 

The proof of Theorem \ref{thm2} is also divided into two parts, in the first part, we construct an auxiliary graph $\Psi$, which is an Eulerian multigraph. In the second part, with the help of $\Psi$, we find a subgraph $T$ of $2*G$, which is an Eulerian multigraph and with all vertices of even degree and at most $2k$. And $T$ is the $k$-walk we want.

In fact, in our proof, we can prove a slight stronger result: the $(\frac{1}{k-1}+\epsilon)$-tough condition is only used when the dominating cliques seuqence defined in Lemma \ref{lm5} has $m=1$. And when the $2K_2$-free graph $G$ has a dominating cliques sequence $\{Q_1,\ldots,Q_m,\ldots,Q_{m+s}\}$ defined as Lemma \ref{lm5} with $m\ge2$, then $\frac{1}{k-1}$-tough condition is good enough to find the $k$-walk. That is:
\begin{theorem}\label{opt}
For any $2K_2$-free graph $G$, if $G$ is $(\frac{1}{k-1}+\epsilon)$-tough, $\epsilon>0$, then $G$ admits a $k$-walk. Additionally, if $G$ has at least two dominating cliques with size at least 3, in a dominating cliques sequence defined as Lemma \ref{lm5}, i.e. $m\ge2$, and if $G$ is $\frac{1}{k-1}$-tough, then $G$ admits a $k$-walk.
\end{theorem}
In the following text, we prove Theorem \ref{opt} instead of Theorem \ref{thm2}.


\subsection{The Construction of $\Psi$}

\subsubsection{Preparation}

Let $G$ be a $(\frac{1}{k-1}+\epsilon)$-tough $2K_2$-free graph, for some $\epsilon>0$. If it has only 2 vertices, this is a trivial case. So, we always consider there are at least 3 vertices. The sequence of cliques defined in Lemma \ref{lm5} is $\{Q_1,\ldots,Q_m,\ldots,Q_{m+s}\}$, where $|Q_i|\ge3$, for $1\le i\le m$ and $|Q_i|=2$ for $m+1\le i\le m+s$. Additionally, $Q_i$ dominates $Q_j$ for $i\le m$ and $i<j$; $Q_i$ weakly dominates $Q_j$ for $m<i<j$. And $Q_{\infty}$ is the induced subgraph of $G$ on all the vertices of $Q_i$, $i>m$, as defind in Lemma \ref{lm6}. Please note it is possible that $s=0$ and $Q_{\infty}$ does not exist in the whole discussion. And if $Q_{\infty}$ does not exist, we can safely skip all the discussion about it in the proof.

First, if $|Q_1|=2$, then $G$ is triangle-free, by Theorem \ref{thm4}, $G$ has a Hamiltonian path, thus $G$ has a $k$-walk for $k\ge2$. So, we always assume $|Q_1|\ge3$ in our proof.

\subsubsection{Finding The Collapsed Matching $M$}
By Theorem \ref{thm4}, there is a spanning path in $Q_{\infty}$, we denote its two endpoint as $v_a$ and $v_b$. $Q_0$ is the induced subgraph of $G$ on all the vertices of all the cliques with size at least 3, as defined in Lemma \ref{lm6}. Now, let us consider the neighbor set of $v_a$ and $v_b$ in $V(Q_0)$. First, neither $N_{Q_0}(v_a)$ nor $N_{Q_0}(v_b)$ is empty, since $Q_{\infty}$ is dominated by all the cliques of size at least 3. If there is only one vertex in $N_{Q_0}(v_a)\cup N_{Q_0}(v_b)$, denote this vertex as $v_{\infty}$. If there are at least two vertices in $N_{Q_0}(v_a)\cup N_{Q_0}(v_b)$, then we can choose two distinct vertices $v'_a,v'_b\in V(Q_0)$ such that $v_av'_a,v_bv'_b\in E(G)$. Please note that if $v_{\infty}$ exist, then there must be only one clique with size at least 3 in the sequence $\{Q_i\}$ we are talking about, i.e. $m=1$.
Recall that $D$ stands for the independent set described in Lemma \ref{lm5} and Lemma \ref{lm6}. 

\begin{case}$m\ge2$\end{case}
If $m\ge2$, then $v_{\infty}$ does not exist. Then we only need the $2K_2$-free graph $G$ to be $\frac{1}{k-1}$-tough, rather than $(\frac{1}{k-1}+\epsilon)$-tough.

For any subset $D_0\subset D$, the neighbor set $N_{G}(D_0)=N_Q(D_0)$ has at least $\frac{|D_0|}{k-1}$ vertices, (that are $\lceil\frac{|D_0|}{k-1}\rceil$ vertices). Otherwise, if $|N_Q(D_0)|<\frac{|D_0|}{k-1}$, after deleting $N_Q(D_0)$, there are at least $|D_0|$ components (isolated vertices), which contradicts with the definition of $\frac{1}{k-1}$-tough. 
Now, split each vertex $v\in Q$ into $k-1$ copies $v_1,\ldots,v_{k-1}$, each of them share the same neighbors with $v$ in $D$ (if it has). And the set of all such split vertices is denoted as $Q'$.  Then each $D_0\subset D$ has at least $|D_0|$ neighbors in $Q'$.
Thus, by Hall' Theorem, there is a matching, namely $M'$, between $V(D)$ and $V(Q')$ covering every vertex in $V(D)$. 
After that, let each group of $k-1$ copies, in $Q'$, split from one vertex, collapse to the original vertex in $Q$. We call the set of these edges in $E(G)$, corresponding to the edges in the matching $M'$, {\bf the collapsed matching $M$}. Then each vertex $v\in Q$ is incident to at most $k-1$ edges in the collapsed matching $M$. 


\begin{case}$m=1$\end{case}
Now, we assume $m=1$. If $v_{\infty}$ does not exist, then everything is same as Case 1.
So, we assmue $v_{\infty}$ exists. Then we use the assumption that $G$ is $(\frac{1}{k-1}+\epsilon)$-tough. For any subset $D_0\subset D$, the neighbor set $N_Q(D_0)$ has at least $(\frac{1}{k-1}+\epsilon)|D_0|$ vertices, (that are $\lfloor\frac{|D_0|}{k-1}\rfloor+1$ vertices).
Now, split each vertex $v\in Q$ into $k-1$ copies $v_1,\ldots,v_{k-1}$, each of them share the same neighbors with $v$ in $D$ (if it has). And the set of all such split vertices is denoted as $Q'$. Then each $D_0\subset D$ has at least $(k-1)(\frac{1}{k-1}+\epsilon)|D_0|\ge|D_0|+1$ neighbors in $Q'$, i.e. $|N_{Q'}(D_0)|\ge|D_0|+1$. Now, denote one of the $k-1$ split copies of $v_{\infty}$ as $v^*_{\infty}$.

Then $|N_{Q'-\{v^*_{\infty}\}}(D_0)|\ge|D_0|$ for every subset $D_0$ in $D$. Thus, by Hall's Theorem, there is a matching, namely $M'$, between $V(D)$ and $V(Q'-\{v^*_{\infty}\})$, covering every vertex in $V(D)$. 
After that, let each group of $k-1$ copies, in $Q'$, split from one vertex collapse to the original vertex in $Q$. We call the set of these edges in $E(G)$, corresponding to the edges in the matching $M'$, the {\bf collapsed matching $M$}. Then each vertex $v\in Q$ may be incident to at most $k-1$ edges from the collapsed matching $M$.
Additionally, when $v_{\infty}$ exist, it is incident to at most $k-2$ edges in the collapsed matching $M$.









\subsubsection{The construction of $\Psi$}
Now, let us construct the auxiliary graph $\Psi$.

First, the vertex set of $\Psi$, $V(\Psi)=\{w_{\infty},w_1,\ldots,w_m\}\cup D'$, each $w_i$, for 
$i=\infty,1,\ldots,m$ corresponds to $Q_{\infty}$ or $Q_i$, for $i=1,\ldots,m$. (Note that if $Q_{\infty}$ does not exist, $w_{\infty}$ does not appear either.) And each vertex $v'_j\in D'$ corresponds to a vertex $v_j\in D$. For each edge $e$ in the collapsed matching $M$, we draw a pair of parallel edges $e'$ and $e''$ on $\Psi$, i.e. if $e=v_iv_j\in E(G)$, with $v_i\in V(D)$ and $v_j\in V(Q_t)$, then we have $e'=v'_iw_t,~e''=v'_iw_t\in E(\Psi)$. We call them {\bf blue edges} in $\Psi$. Note that the degrees of vertices in $\Psi$ count parallel edges with multiplicity.


Now, we connect all the vertices in $\{w_i;i=\infty,1,\ldots,m\}$, by a circle of {\bf red edges}. For convenience, let the red edges be $$w_1w_2,~w_2w_3,\ldots,w_{m-1}w_m,~w_mw_{\infty},~w_{\infty}w_1.$$

 Note there are two trivial cases:
\begin{enumerate}
\item if there is only one $\{w_i\}$, namely $w_1$, then there is no red edge.
\item if there are only two vertices in $\{w_i\}$, then the circle is just a pair of parallel edges.
\end{enumerate}

Then we finish the construction of $\Psi$. Obviously, $\Psi$ is connected multigraph, with all vertex degree even. Thus, $\Psi$ is Eulerian.







\subsection{The Construction of $T$}


Now, with the help of $\Psi$, we are going to find a spanning subgraph $T$ of $2*G$.

First, the vertex set of $T$, is set to be the vertex set of $G$.

\subsubsection{
Finding first-class edges in $T$}
The set of {\bf first-class edges} in $T$ is just doubling all the edges in the collapsed matching $M$. So, there is a one to one corresponding between the first-class edges and the blue edges.



\subsubsection{
Finding second-class edges in $T$}
If $Q_{\infty}$ and $w_{\infty}$ exist, we first look for the {\bf second-class edges} corresponding to the two red edges incident to $w_{\infty}$ (if $Q_{\infty}$ and $w_{\infty}$ do not exist, we directly go to the process of finding second-class edges between cliques of size at least 3).


Recall that the name of the two endpoint of the spanning path in $Q_{\infty}$ are $v_a$ and $v_b$, as the discussion before.

If in $\Psi$, $w_{\infty}$ is adjacent to two distinct vertices $w_1$ and $w_m$, then we can find a vertex $v'_a\in V(Q_1)$ and a vertex $v'_b\in V(Q_m)$ such that $v_av_a',v_bv_b'\in E(G)$, since $Q_{\infty}$ is dominated by both $Q_1$ and $Q_m$. We call $v_av_a'$ and $v_bv_b'$ {\bf second-class edges}.

If in $\Psi$, $w_{\infty}$ is adjacent to only one vertex $w_1$, and if there are two distinct vertices $v_a'$ and $v_b'$ in $V(Q_1)$ such that $v_av_a',v_bv_b'\in E(G)$, then we choose $v_av_a'$ and $v_bv_b'$ to be the {\bf second-class edges} we want. If there is only one vertex in $Q_1$ which is adjacent to $v_a$ and $v_b$ in $G$, recall that we have already named it as $v_{\infty}$, and there are at most $k-2$ edges in the collapsed matching $M$ connect to it. Then we select $v_av_{\infty}$ and $v_bv_{\infty}$ into $T$ as {\bf second-class edges}. Please note this is the {\bf only case} where we allow two second-class edges connecting to one vertex in $T$.





After two second-class edges incident to $Q_{\infty}$ are found, we go on to look for the second-class edges between the cliques of size at least 3.
For any red edge $w_iw_{i+1}$, we want to realize it into $T$ as a {\bf second-class edge}. Let us look at $Q_{i+1}$ first. We know that $w_{i+1}$ is incident to two red edges, so, there is only one vertex in $Q_{i+1}$, say $v_{i+1,1}$, is connected to another second-class edge. And $|Q_{i+1}|\ge3$, so there are at least two vertices in $Q_{i+1}$, say $v_{i+1,2}$ and $v_{i+1,3}$, are not incident to any second-class edge at this moment. Both of them are dominated by $Q_i$. Then we claim that $v_{i+1,2}$ and $v_{i+1,3}$ have at least two neighbors in $Q_i$. Otherwise, assuming $v_{i+1,2}$ and $v_{i+1,3}$ have only one neighbor in $Q_i$, we know $|Q_i|\ge3$, so there are at least two vertices, say $v_{i,1}$ and $v_{i,2}$, who are adjacent to neither $v_{i+1,2}$ nor $v_{i+1,3}$. Then $v_{i+1,2}v_{i+1,3}$ and $v_{i,1}v_{i,2}$ form a $2K_2$. Contradiction. Now, we can denote $v_{i+1,2}v_1,~v_{i+1,3}v_2\in E(G)$, where $v_1,v_2\in Q_i$. What is more, in $v_1$ and $v_2$, there is at most one of them, say $v_1$ is incident to another second-class edge, since there are only two second-class edges connected on $Q_i$. Then we select $v_{i+1,3}v_2$ into $T$ as a {\bf second-class edge}.











\subsubsection{
Finding third-class edges in $T$}

The final step in the construction is to find some so-called {\bf third-class edges} in $T$. After adding all the first- and second-class edges, let us look at each $Q_i$, where $i=1,\ldots,m$.

First, assuming $v_{\infty}$ exists, there is only $Q_1$ for us to work on. In $Q_1$, we just connect all its vertices by a circle of {\bf third-class edges}. Then every vertex has even degree and at most $2k$, since each vertex is incident to 2 third-class edges. And $v_{\infty}$ is incident to two second-class edges and at most $k-2$ pairs of first-class edges, while other vertices may be incident to at most $k-1$ pairs of first-class edges.

Now, we assume $v_{\infty}$ does not exist. Then, in $Q_i$, there are two vertices, say $v_s$ and $v_e$, who are incident to second-class edges. We draw a spanning path with one endpoint $v_s$ and another endpoint $v_e$. All the edges in this path are called {\bf third-class edges}.
Now each vertex has even degree which is at most $2k$. Because for each endpoint, it has one third-class edge, one second-class edge, and at most $k-1$ pairs of first class edges. And for each inner vertex, it is incident to two third-class edges and at most $k-1$ pairs of first-class edges.



After drawing all these first-, second- and third-class edges on $T$, we observe that:
\begin{enumerate}
\item $T$ is connected multigraph.
\item $T$ is a subgraph of $2*G$.
\item each vertex in $T$ has even degree of at most $2k$, where the degree of parallel edges is counted with multiplicity.
\end{enumerate}
We conclude that $T$ is Eulerian, and a $k$-walk in $G$.\qed



At last we pose two conjectures to finish this paper:


\begin{conjecture}
Every $3/2$-tough $2K_2$-free graph on at least three vertices has a 2-trail, i.e. a 2-walk with each edge appearing in the walk at most once.
\end{conjecture}


\begin{conjecture}
Every 2-tough $2K_2$-free graph on at least three vertices is Hamiltonian.
\end{conjecture}
























\bibliography{reftough}

\bibliographystyle{plain}






\end{document}
